---
title: "Supporting Tables ANOVA"
author: "Daniel Stern"
date: "2024-04-19"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressPackageStartupMessages({
  library(dplyr)
  library(flextable)
  library(officer)
})
```

```{r calcs}

load("output/tables.RData")
```

## Results of three-way ANOVA

Supporting Table. Results of three-way ANOVA for the Acute dataset on IgG data.
```{r anovaAcuteIgG}
(   anovaAcuteIgG
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(2:3), digits = 0 ) 
    %>% colformat_double(j = c(4:7), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Results of three-way ANOVA for the Acute dataset on IgM data.
```{r anovaAcuteIgM}
(   anovaAcuteIgM
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(2:3), digits = 0 ) 
    %>% colformat_double(j = c(4:7), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Results of three-way ANOVA for the Epi dataset on IgG data.
```{r anovaEpiIgG}
(   anovaEpiIgG
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(2:3), digits = 0 ) 
    %>% colformat_double(j = c(4:7), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Results of three-way ANOVA for the Epi dataset on IgM data.
```{r anovaAEpiIgM}
(   anovaEpiIgM
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(2:3), digits = 0 ) 
    %>% colformat_double(j = c(4:7), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```



## Simple main effects for the difference between the three serostatuses (pre, MVA, Mpox)

Supporting Table. Simple main effects for the difference between the three serostatuses (pre, MVA, Mpox)
in depence on the antigen on the Acute dataset using IgG data.
```{r simplesimpleAcuteIgG}
(   simplesimpleAcuteIgG
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(4:5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Simple main effects for the difference between the three serostatuses (pre, MVA, Mpox)
in depence on the antigen on the Acute dataset using IgM data.
```{r simplesimpleAcuteIgM}
(   simplesimpleAcuteIgM
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(4:5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Simple main effects for the difference between the three serostatuses (pre, MVA, Mpox)
in depence on the antigen on the Epi dataset using IgG data.
```{r simplesimpleEpiIgG}
(   simplesimpleEpiIgG
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(4:5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Simple main effects for the difference between the three serostatuses (pre, MVA, Mpox)
in depence on the antigen on the Epi dataset using IgM data.
```{r simplesimpleEpiIgM}
(   simplesimpleEpiIgM
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(4:5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```





## Pairwise comparisons

Supporting Table. Pairwise comparisons on the Acute dataset using IgG data.
```{r pairwiseIgG}
(   pairwiseAcuteIgG
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table.Pairwise comparisons on the Acute dataset using IgM data.
```{r pairwiseAcuteIgM}
(   pairwiseAcuteIgM
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Pairwise comparisons on the Epi dataset using IgG data.
```{r pairwiseEpiIgG}
(   pairwiseEpiIgG
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```


Supporting Table. Pairwise comparisons on the Epi dataset using IgM data.
```{r pairwiseEpiIgM}
(   pairwiseEpiIgM
    %>% flextable()
    #%>% set_header_labels( Effect = "Tree Age (days)"
    #                     , DFn = "Mean trunk circumference (mm)"
    #                     , Dfd = "SD of trunk circumference (mm)"
    #                     )
    %>% hline_bottom( part = "header"
                      , border = fp_border_default( width = 0.5 ) # inches
    )
    %>% colformat_double(j = c(5), digits = 0 ) 
    %>% colformat_double(j = c(6:9), digits = 2 )
    %>% width( j = 2:3, width = 1.5 ) # inches
)
```




